---
title: "Experiments 2 & 3: Demographics & Exclusions"
pagetitle: "exp 2-3 | exclusions"
author: "Owen Morgan"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document
---

<style type="text/css">
  body{
  font-family: Avenir;
  font-size: 12pt;
}
</style>

**Summary**. We have recruited 366 right handers, and 1084 "left" and "mixed" handers. Of these, 357 right (98%), 685 left, and 288 mixed handers (90%) completed the experiment. 

529 EHI left handers, 171 mixed handers, and 413 right handers meet inclusion criteria for Navon.

342 EHI left handers, 99 mixed handers, and 293 right handers meet inclusion criteria for both Navon and Dichotic listening.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      fig.align = "center", fig.width = 9,
                      fig.height = 6)
options(knitr.kable.NA = "")

cli.progress_show_after <- 0

# Suppress summarise info
options(dplyr.summarise.inform = FALSE)
```

```{r lib}
library(here)
library(tidyverse)
library(cli) # For printing error messages
library(knitr) # for printing figures

library(gt)

source(here::here("lib", "util.R"))
source(here::here("lib", "demographics.R"))

EXPERIMENT_DIR <- "experiments_2-3"
source(here::here(EXPERIMENT_DIR, "lib", "load_process", "load_process.R"))

## Colors for plots
plot_blue <- c("#337aB7")
plot_colors <- c("#4477AA",
                 "#EE6677",
                 "#CCBB44",
                 "#66CCEE",
                 "#AA3377",
                 "#228833",
                 "#BBBBBB")
```

```{r config}
data_dir <- here::here(EXPERIMENT_DIR, "data")
input_dir <- here::here(data_dir, "input_exp_n1450")
proc_dir <- here::here(data_dir, "proc_exp_n1450")
fig_dir <- here::here(EXPERIMENT_DIR, "figures")
n_recruited = 1450 ## Total recruited + paid. For reporting exclusions

use_cached_demofigs = FALSE
```

```{r load_combined, include = F}
## Load pre-exclusion combined trial-per-row data, subset columns
aah_navon_all <- load_navon_all(proc_dir)

## Load pre-exclusion summary data (includes DL data), subset columns, and recode "ehi_total" to "ehi."
aah_summary_all <- load_summary_all(proc_dir)
```

```{r prepare}
## Combine prolific demographic/prescreener data with summary data

## Load Prolific's handedness screening data
prolific_data_dir <- here::here(input_dir, "prolific")

## Paths to Experiment 2 & 3 prolific data
path_E2_exp_10RH <- "E2_exp_10RH_prolific_export_64626d237f28021d02c46b88.csv"
path_E2_exp_356RH <- "E2_exp_356RH_prolific_export_64627d85b57d4ca484b09c41.csv"
path_E2_exp_231LH <- "E2_exp_231LH_prolific_export_6487624e53e6e5976dcfd077.csv"
path_E2_exp_77LH <- "E2_exp_VT_77LH_prolific_export_6494fe8f198463398ffc8ffd.csv"
path_E2_exp_355LH <- "E2_exp_VT_355LH_prolific_export_6499f70caf303cfd6821adef.csv"
path_E2_exp_421LH <- "E2_exp_421LH_prolific_export_6494f989acc551f18bbce523.csv"

pdata_E2_exp_10RH <- read_prolific_data(here(prolific_data_dir, path_E2_exp_10RH)) |> 
  mutate(sample = "10 pilot righties", sample2 = "All righties")
pdata_E2_exp_356RH <- read_prolific_data(here(prolific_data_dir, path_E2_exp_356RH)) |> 
  mutate(sample = "356 righties", sample2 = "All righties")
pdata_E2_exp_231LH <- read_prolific_data(here(prolific_data_dir, path_E2_exp_231LH)) |> 
  mutate(sample = "231 lefties", sample2 = "All lefties")
pdata_E2_exp_77LH <- read_prolific_data(here(prolific_data_dir, path_E2_exp_77LH)) |> 
  mutate(sample = "77 lefties", sample2 = "All lefties")
pdata_E2_exp_355LH <- read_prolific_data(here(prolific_data_dir, path_E2_exp_355LH)) |> 
  mutate(sample = "355 lefties", sample2 = "All lefties")
pdata_E2_exp_421LH <- read_prolific_data(here(prolific_data_dir, path_E2_exp_421LH)) |> 
  mutate(sample = "421 lefties", sample2 = "All lefties")

prolific_data <-
  bind_rows(pdata_E2_exp_10RH,
            pdata_E2_exp_356RH,
            pdata_E2_exp_231LH,
            pdata_E2_exp_77LH,
            pdata_E2_exp_355LH,
            pdata_E2_exp_421LH,
            ) |>
  rename(subject = `Participant id`,
         prolific_handedness = Handedness) |>
  mutate(
    prolific_handedness = prolific_handedness |> recode(
      `Right-handed` = "Right",
      `Left-handed` = "Left",
      `Ambidextrous` = "Mixed"
    ) |> as.factor() |> droplevels()
  ) |>
  select(subject, sample, sample2, prolific_handedness)

## Add prolific handedness to dataset
aah_summary_all <-
  aah_summary_all |> left_join(prolific_data, by = "subject")
### Code handedness
aah_summary_all <- aah_summary_all |>
  mutate(handedness = case_when(ehi <= -40 ~ "Left",
                                ehi >= 40 ~ "Right",
                                ehi > -40 & ehi < 40 ~ "Mixed"))

```

## {.tabset}

### Recruitment & Exclusions {.tabset .tabset-pills}

```{r make_exclusions}
## Calculate any exclusions not based on Navon task data.
##   (Exclusions based on Navon task data are specified in:
##    1_process.Rmd, calling load_process.R/summarize_ind())
##       Responded "go" almost every time (78/80 or more)?
##       Accuracy at 60% or lower on any main block?
##       Median RT over 1500 or under 200?
##       Took longer than 45 minutes to do the task? (Should delete this one - not preregistered, don't know why we included it.
## Exclusions not based on Navon task data:
##   Dichotic listening exclusions (sound checks, accuracy)
##   Demographics exclusions that slipped through pre-screener:
##     Country (non-us); Age (not between 18 and 40)
##   Failed "Have you done this task before"
##   Has task data, but no EHI data. (e.g., if they quit inquisit after task)
##   EHI handedness does not match pre-screener


#### UNIVERSAL EXCLUSIONS

## Mark exclusion if visually identified outlier
## 1330
aah_summary_all <- aah_summary_all |> 
  mutate(exclude_visual = case_when(
    subject == "5eee761287fdd331fc618449" ~ 1,
    TRUE ~ 0
    )
  )

## Mark exclusion if country is not "US"
aah_summary_all <- aah_summary_all |>
  mutate(exclude_country = case_when(
    country %in% c("US", "UK") ~ 0,
    TRUE ~ 1,)
    )

## Mark exclusion if age is not between 18 and 40
aah_summary_all <- aah_summary_all |>
  mutate(exclude_age = case_when(
    age >=18 & age <= 40 ~ 0,
    TRUE ~ 1
  ))

## Mark exclusion if failed "Have you done this task before?"
aah_summary_all <- aah_summary_all |> 
  mutate(exclude_done_before = case_when(
    task_experience_response == "No" ~ 0,
    task_experience_response == "Yes" ~ 1,
    TRUE ~ 0 # do not exclude people who did not complete the question
  ))


## Mark exclusion if no EHI (if EHI is not between -100 & 100)
aah_summary_all <- aah_summary_all |>
  mutate(exclude_no_ehi = case_when(
    ehi >= -100 & ehi <= 100 ~ 0,
    TRUE ~ 1
  ))

## Mark exclusion if EHI response does not match pre-screened handedness
##  Remove pre-screen lefties with EHI > 0; Remove pre-screen ambis with EHI == 100 or -100; Remove pre-screen righties with handedness < 0.
aah_summary_all <- aah_summary_all |>
  mutate(exclude_ehi_mismatch = case_when(
    prolific_handedness == "Left" & ehi >= 0 ~ 1,
    prolific_handedness == "Mixed" & (ehi == 100 | ehi == -100) ~ 1,
    prolific_handedness == "Right" & ehi <= 0 ~ 1,
    TRUE ~ 0
  ))

#### DICHOTIC LISTENING EXCLUSIONS
#### Calculate and mark dichotic listening exclusions

## Mark headphone check exclusions (less than 5/6)
aah_summary_all <- aah_summary_all |> 
  mutate(exclude_headphone_check = case_when(
    headphonecheck_nCorrect < 5 ~ 1,
    TRUE ~ 0
  ))

## Mark stereo audio check exclusions (less than 5/6)
aah_summary_all <- aah_summary_all |> 
  mutate(exclude_stereo_check = case_when(
    stereocheck_nCorrect < 5 ~ 1,
    TRUE ~ 0
  ))

## Mark mono trial accuracy exclusions
aah_summary_all <- aah_summary_all |> 
  mutate(exclude_DL_mono_acc = case_when(
    DL_monoPctCorrect < 75 ~ 1,
    TRUE ~ 0
  ))

## Mark stereo trial accuracy exclusions
aah_summary_all <- aah_summary_all |> 
  mutate(exclude_DL_dual_acc = case_when(
    DL_dualPctCorrect < 60 ~ 1,
    TRUE ~ 0
  ))

aah_summary_all <- aah_summary_all |>
  mutate(
    exclude_dl = case_when(
      exclude_country == 1 ~ 1,
      exclude_age == 1 ~ 1,
      exclude_done_before == 1 ~ 1,
      exclude_no_ehi == 1 ~ 1,
      exclude_ehi_mismatch == 1 ~ 1,
      exclude_headphone_check == 1 ~ 1,
      exclude_stereo_check == 1 ~ 1,
      exclude_DL_mono_acc == 1 ~ 1,
      exclude_DL_dual_acc == 1 ~ 1,
      TRUE ~ 0
    )
  )

#### NAVON EXCLUSIONS

## Update "exclude" column.
aah_summary_all <- aah_summary_all |>
  mutate(
    exclude_navon = case_when(
      exclude_many_gos == 1 ~ 1,
      exclude_low_acc == 1 ~ 1,
      exclude_low_rt == 1 ~ 1,
      exclude_high_rt == 1 ~ 1,
      exclude_country == 1 ~ 1,
      exclude_age == 1 ~ 1,
      exclude_done_before == 1 ~ 1,
      exclude_no_ehi == 1 ~ 1,
      exclude_ehi_mismatch == 1 ~ 1,
      exclude_visual == 1 ~ 1,
      TRUE ~ 0
    )
  )

#### ANY EXCLUSIONS
aah_summary_all <- aah_summary_all |>
  mutate(
    exclude_any = case_when(
      exclude_many_gos == 1 ~ 1,
      exclude_low_acc == 1 ~ 1,
      exclude_low_rt == 1 ~ 1,
      exclude_high_rt == 1 ~ 1,
      exclude_headphone_check == 1 ~ 1,
      exclude_stereo_check == 1 ~ 1,
      exclude_DL_mono_acc == 1 ~ 1,
      exclude_DL_dual_acc == 1 ~ 1,
      exclude_country == 1 ~ 1,
      exclude_age == 1 ~ 1,
      exclude_done_before == 1 ~ 1,
      exclude_no_ehi == 1 ~ 1,
      exclude_ehi_mismatch == 1 ~ 1,
      exclude_visual == 1 ~ 1,
      TRUE ~ 0
    )
  )

## Create long dataset with all subjects (included and excluded)
aah_long_all <- left_join(aah_navon_all, aah_summary_all) %>% 
  ## filter columns to match E1 long dataset
  select(
    -ehi_i1_writing,
    -ehi_i2_throwing,
    -ehi_i3_toothbrush,
    -ehi_i4_spoon
  )
           
aah_summary_all_filtered <- aah_summary_all %>% 
  select(
    -ehi_i1_writing,
    -ehi_i2_throwing,
    -ehi_i3_toothbrush,
    -ehi_i4_spoon
  )

## Save long table with columns for all exclusion reasons.
## This is "the data."
readr::write_tsv(aah_long_all, here(proc_dir, "aah_long.tsv"))
readr::write_tsv(aah_summary_all_filtered, here(proc_dir, "aah_summary.tsv"))

## Create long data tables with inclusions only
aah <- aah_long_all |> filter(exclude_any == 0)
aah_navon <- aah_long_all |> filter(exclude_navon == 0)
aah_dl <- aah_long_all |> filter(exclude_dl == 0)

## Create summary table with inclusions only, and handedness coded
aah_summary_all <- aah_summary_all |> mutate(
  handedness = case_when(
    ehi <= -40 ~ "Left",
    ehi >= 40 ~ "Right",
    ehi > -40 & ehi < 40 ~ "Mixed"
  )
)

aah_summary <- aah_summary_all |> filter(exclude_any == 0)
aah_summary_navon <- aah_summary_all |> filter(exclude_navon == 0)
aah_summary_dl <- aah_summary_all |> filter(exclude_dl == 0)
```


#### Everyone
<br>

##### Exclusions: Any reason
<br>
```{r describe_exclusions_1}
n_all <- aah_summary_all$subject |> unique() |> length()
n_exclusions <- aah_summary_all$exclude_any |> sum()
n_keepers <- aah_summary_all |>
  filter(exclude_any == 0) |>
  (\(.) .[["subject"]])() |>
  unique() |>
  length()
tibble(
  "n (recruited)" = n_recruited,
  "n (with full task data)" = n_all,
  "exclusions" = n_exclusions,
  "n (keepers)" = n_keepers) |> 
  pretty_table()
```
<br>
We have recruited `r n_recruited` participants through prolific. Of these, `r n_all` completed the task phase of the experiment.
<br>
<br>
`r n_exclusions` were excluded for the reasons described below, leaving `r n_keepers` keepers.
<br>
```{r}
## Check number of participants excluded for multiple reasons
aah_summary_all |> 
  select(subject, exclude_country, exclude_age, exclude_done_before, exclude_no_ehi, exclude_ehi_mismatch, exclude_visual,
         exclude_many_gos, exclude_low_acc, exclude_low_rt, exclude_high_rt,
         exclude_headphone_check, exclude_stereo_check, exclude_DL_mono_acc, exclude_DL_dual_acc) |> 
  mutate(n_exclusion_reasons = rowSums(across(starts_with("exclude")))) |> 
  group_by(n_exclusion_reasons) |> 
  summarize(n_subjects = n()) |> 
  pretty_table("How many subjects were excluded for multiple reasons?")
```
<br>
```{r describe_exclusions_2}
exclusion_tbl <- aah_summary_all |> 
  rename(any = exclude_any) |> 
  select(any, subject, exclude_country, exclude_age, exclude_done_before, exclude_no_ehi, exclude_ehi_mismatch, exclude_visual,
         exclude_many_gos, exclude_low_acc, exclude_low_rt, exclude_high_rt,
         exclude_headphone_check, exclude_stereo_check, exclude_DL_mono_acc, exclude_DL_dual_acc) |> 
summarize(across(starts_with("exclude"), sum)) |> 
pivot_longer(cols = everything(), 
             names_to = 'exclusion', values_to = "n",
             names_prefix = "exclude_") |> 
  mutate('exclusion' = recode(exclusion,
    any = "Any",
    country = "Non-US/UK country",
    age = "Age outside 18-40",
    done_before = "Reported having done the task before",
    high_rt = "Navon: High RT (median > 1500ms)",
    low_rt = "Navon: Low RT (median < 200ms)",
    low_acc = "Navon: Low accuracy (below 60% on any block)",
    many_gos = "Navon: Too many 'gos' (78/80 trials or more)",
    no_ehi = "Quit before completing EHI",
    ehi_mismatch = "Prescreener/EHI mismatch",
    headphone_check = "Dichotic listening: Failed headphone check (<5/6)",
    stereo_check = "Dichotic listening: Failed stereo check (<5/6)",
    DL_mono_acc = "Dichotic listening: low mono accuracy (<75%)",
    DL_dual_acc = "Dichotic listening: low dual accuracy (<60%)",
    visual = "Outlier based on visual inspection"
  )) |> 
  arrange(-n, exclusion) |> 
  select(n, exclusion) |> 
  rename('Reason for exclusion' = exclusion)

# exclusion_tbl
exclusion_tbl |> pretty_table()
```
<br>

##### Exclusions: Navon
<br>
```{r}
n_all <- aah_summary_all$subject |> unique() |> length()
n_exclusions <- aah_summary_all$exclude_navon |> sum()
n_keepers <- aah_summary_all |>
  filter(exclude_navon == 0) |>
  (\(.) .[["subject"]])() |>
  unique() |>
  length()
tibble(
  "n (recruited)" = n_recruited,
  "n (with full task data)" = n_all,
  "exclusions" = n_exclusions,
  "n (keepers)" = n_keepers) |> 
  pretty_table()
```
<br>
`r n_exclusions` were excluded for the reasons described below, leaving `r n_keepers` keepers.
<br>
```{r}
## Check number of participants excluded for multiple reasons
aah_summary_all |> 
  select(subject, exclude_country, exclude_age, exclude_done_before, exclude_no_ehi, exclude_ehi_mismatch, exclude_visual,
         exclude_many_gos, exclude_low_acc, exclude_low_rt, exclude_high_rt) |> 
  mutate(n_exclusion_reasons = rowSums(across(starts_with("exclude")))) |> 
  group_by(n_exclusion_reasons) |> 
  summarize(n_subjects = n()) |> 
  pretty_table("How many subjects were excluded for multiple reasons?")
```
<br>
```{r }
exclusion_tbl <- aah_summary_all |> 
  rename(any = exclude_navon) |> 
  select(any, subject, exclude_country, exclude_age, exclude_done_before, exclude_no_ehi, exclude_ehi_mismatch, exclude_visual,
         exclude_many_gos, exclude_low_acc, exclude_low_rt, exclude_high_rt) |> 
summarize(across(starts_with("exclude"), sum)) |> 
pivot_longer(cols = everything(), 
             names_to = 'exclusion', values_to = "n",
             names_prefix = "exclude_") |> 
  mutate('exclusion' = recode(exclusion,
    any = "Any",
    country = "Non-US/UK country",
    age = "Age outside 18-40",
    done_before = "Reported having done the task before",
    high_rt = "Navon: High RT (median > 1500ms)",
    low_rt = "Navon: Low RT (median < 200ms)",
    low_acc = "Navon: Low accuracy (below 60% on any block)",
    many_gos = "Navon: Too many 'gos' (78/80 trials or more)",
    no_ehi = "Quit before completing EHI",
    ehi_mismatch = "Prescreener/EHI mismatch",
    headphone_check = "Dichotic listening: Failed headphone check (<5/6)",
    stereo_check = "Dichotic listening: Failed stereo check (<5/6)",
    DL_mono_acc = "Dichotic listening: low mono accuracy (<75%)",
    DL_dual_acc = "Dichotic listening: low dual accuracy (<60%)",
    visual = "Outlier based on visual inspection"
  )) |> 
  arrange(-n, exclusion) |> 
  select(n, exclusion) |> 
  rename('Reason for exclusion' = exclusion)

exclusion_tbl |> pretty_table()
```
<br>


##### Exclusions: Dichotic Listening
<br>
```{r}
n_all <- aah_summary_all$subject |> unique() |> length()
n_exclusions <- aah_summary_all$exclude_dl |> sum()
n_keepers <- aah_summary_all |>
  filter(exclude_dl == 0) |>
  (\(.) .[["subject"]])() |>
  unique() |>
  length()
tibble(
  "n (recruited)" = n_recruited,
  "n (with full task data)" = n_all,
  "exclusions" = n_exclusions,
  "n (keepers)" = n_keepers) |> 
  pretty_table()
```
<br>
`r n_exclusions` were excluded for the reasons described below, leaving `r n_keepers` keepers.
<br>
```{r}
## Check number of participants excluded for multiple reasons
aah_summary_all |> 
  select(subject, exclude_country, exclude_age, exclude_done_before, exclude_no_ehi, exclude_ehi_mismatch,
         exclude_headphone_check, exclude_stereo_check, exclude_DL_mono_acc, exclude_DL_dual_acc) |> 
  mutate(n_exclusion_reasons = rowSums(across(starts_with("exclude")))) |> 
  group_by(n_exclusion_reasons) |> 
  summarize(n_subjects = n()) |> 
  pretty_table("How many subjects were excluded for multiple reasons?")
```
<br>
```{r}
exclusion_tbl <- aah_summary_all |> 
  rename(any = exclude_dl) |> 
  select(subject, exclude_country, exclude_age, exclude_done_before, exclude_no_ehi, exclude_ehi_mismatch,
         exclude_headphone_check, exclude_stereo_check, exclude_DL_mono_acc, exclude_DL_dual_acc) |> 
summarize(across(starts_with("exclude"), sum)) |> 
pivot_longer(cols = everything(), 
             names_to = 'exclusion', values_to = "n",
             names_prefix = "exclude_") |> 
  mutate('exclusion' = recode(exclusion,
    any = "Any",
    country = "Non-US/UK country",
    age = "Age outside 18-40",
    done_before = "Reported having done the task before",
    high_rt = "Navon: High RT (median > 1500ms)",
    low_rt = "Navon: Low RT (median < 200ms)",
    low_acc = "Navon: Low accuracy (below 60% on any block)",
    many_gos = "Navon: Too many 'gos' (78/80 trials or more)",
    no_ehi = "Quit before completing EHI",
    ehi_mismatch = "Prescreener/EHI mismatch",
    headphone_check = "Dichotic listening: Failed headphone check (<5/6)",
    stereo_check = "Dichotic listening: Failed stereo check (<5/6)",
    DL_mono_acc = "Dichotic listening: low mono accuracy (<75%)",
    DL_dual_acc = "Dichotic listening: low dual accuracy (<60%)"
  )) |> 
  arrange(-n, exclusion) |> 
  select(n, exclusion) |> 
  rename('Reason for exclusion' = exclusion)

# exclusion_tbl
exclusion_tbl |> pretty_table()
```
<br>
```{r}
aah_summary_all |> group_by(headphonecheck_nCorrect) |> 
  summarize(n = n()) |> arrange(desc(n)) |> 
  pretty_table("Distribution of headphone check accuracy (which sound was the quietest?)")
```
<br>
```{r}
aah_summary_all |> group_by(stereocheck_nCorrect) |> 
  summarize(n = n()) |> arrange(desc(n)) |> 
  pretty_table("Distribution of stereo check accuracy (did the sound play to the right or left ear?)")
```
<br>

#### By handedness group

All recruits before exclusions.
```{r demo_allrecruits_grouped}
aah_summary_all |>
  group_by(handedness) |> 
  demo_summary_table() |> 
  pretty_table("All recruits (before exclusions)")
```
<br>
```{r}
aah_summary_all |> group_by(prolific_handedness) |> 
  summarize(n = n(),
            `Any exclusion` = sum(exclude_any),
            Navon = sum(exclude_navon),
            DL = sum(exclude_dl),
            `EHI mismatch` = sum(exclude_ehi_mismatch)) |> 
  pretty_table("Exclusions by Prolific handedness group")
```
<br>
<br>
```{r}
aah_summary_all |> group_by(handedness) |> 
  summarize(n = n(),
            `Any exclusion` = sum(exclude_any),
            Navon = sum(exclude_navon),
            DL = sum(exclude_dl),
            `EHI mismatch` = sum(exclude_ehi_mismatch)) |> 
  pretty_table("Exclusions by EHI handedness group")
```
<br>

**Exclusions by Prolific handedness**
<br>
```{r}
counts <- aah_summary_all |> group_by(prolific_handedness) |> count()
n_recruited_left <- counts |> filter(prolific_handedness == "Left") |> pull(n)
n_recruited_mixed <- counts |> filter(prolific_handedness == "Mixed") |> pull(n)
n_recruited_right <- counts |> filter(prolific_handedness == "Right") |> pull(n)
```
<br>
Right handers (n recruited = `r n_recruited_right`)
```{r describe_exclusions_2_grouped_pR}
exclusion_tbl <- aah_summary_all |>
  filter(prolific_handedness == "Right") |>
  rename(exclude_any = exclude_any) |>
summarize(across(starts_with("exclude"), sum)) |>
pivot_longer(cols = everything(),
             names_to = 'exclusion', values_to = "n",
             names_prefix = "exclude_") |>
  mutate('exclusion' = recode(exclusion,
    any = "Any",
    country = "Non-US country",
    age = "Age outside 18-40",
    done_before = "Reported having done the task before",
    high_rt = "Navon: High RT (median > 1500ms)",
    low_rt = "Navon: Low RT (median < 200ms)",
    low_acc = "Navon: Low accuracy (below 60% on any block)",
    many_gos = "Navon: Too many 'gos' (78/80 trials or more)",
    no_ehi = "Quit before completing EHI",
    ehi_mismatch = "Prescreener/EHI mismatch",
    headphone_check = "Failed headphone check (<5/6)",
    stereo_check = "Failed stereo check (<5/6)",
    DL_mono_acc = "Dichotic listening: low mono accuracy (<75%)",
    DL_dual_acc = "Dichotic listening: low dual accuracy (<60%)"
  )) |>
  arrange(-n, exclusion) |>
  select(n, exclusion) |>
  rename('Reason for exclusion' = exclusion,
         "n (Right)" = n)

# exclusion_tbl
exclusion_tbl |> pretty_table()
```
<br>
Mixed handers (n recruited = `r n_recruited_mixed`)
```{r describe_exclusions_2_grouped_pM}
exclusion_tbl <- aah_summary_all |>
  filter(prolific_handedness == "Mixed") |>
  rename(exclude_any = exclude_any) |>
summarize(across(starts_with("exclude"), sum)) |>
pivot_longer(cols = everything(),
             names_to = 'exclusion', values_to = "n",
             names_prefix = "exclude_") |>
  mutate('exclusion' = recode(exclusion,
    any = "Any",
    country = "Non-US country",
    age = "Age outside 18-40",
    done_before = "Reported having done the task before",
    high_rt = "Navon: High RT (median > 1500ms)",
    low_rt = "Navon: Low RT (median < 200ms)",
    low_acc = "Navon: Low accuracy (below 60% on any block)",
    many_gos = "Navon: Too many 'gos' (78/80 trials or more)",
    no_ehi = "Quit before completing EHI",
    ehi_mismatch = "Prescreener/EHI mismatch",
    headphone_check = "Failed headphone check (<5/6)",
    stereo_check = "Failed stereo check (<5/6)",
    DL_mono_acc = "Dichotic listening: low mono accuracy (<75%)",
    DL_dual_acc = "Dichotic listening: low dual accuracy (<60%)"
  )) |>
  arrange(-n, exclusion) |>
  select(n, exclusion) |>
  rename('Reason for exclusion' = exclusion,
         "n (Mixed)" = n)

exclusion_tbl |> pretty_table()
```
<br>
Left handers (n recruited = `r n_recruited_left`)
```{r describe_exclusions_2_grouped_pL}
exclusion_tbl <- aah_summary_all |>
  filter(prolific_handedness == "Left") |>
  rename(exclude_any = exclude_any) |>
summarize(across(starts_with("exclude"), sum)) |>
pivot_longer(cols = everything(),
             names_to = 'exclusion', values_to = "n",
             names_prefix = "exclude_") |>
  mutate('exclusion' = recode(exclusion,
    any = "Any",
    country = "Non-US country",
    age = "Age outside 18-40",
    done_before = "Reported having done the task before",
    high_rt = "Navon: High RT (median > 1500ms)",
    low_rt = "Navon: Low RT (median < 200ms)",
    low_acc = "Navon: Low accuracy (below 60% on any block)",
    many_gos = "Navon: Too many 'gos' (78/80 trials or more)",
    no_ehi = "Quit before completing EHI",
    ehi_mismatch = "Prescreener/EHI mismatch",
    headphone_check = "Failed headphone check (<5/6)",
    stereo_check = "Failed stereo check (<5/6)",
    DL_mono_acc = "Dichotic listening: low mono accuracy (<75%)",
    DL_dual_acc = "Dichotic listening: low dual accuracy (<60%)"
  )) |>
  arrange(-n, exclusion) |>
  select(n, exclusion) |>
  rename('Reason for exclusion' = exclusion,
         "n (Left)" = n)

exclusion_tbl |> pretty_table()
```
<br>
**Exclusions by EHI handedness**
<br>
```{r}
counts <- aah_summary_all |> group_by(handedness) |> count()
n_ehi_left <- counts |> filter(handedness == "Left") |> pull(n)
n_ehi_mixed <- counts |> filter(handedness == "Mixed") |> pull(n)
n_ehi_right <- counts |> filter(handedness == "Right") |> pull(n)
```
<br>
Right handers (n = `r n_ehi_right`)
```{r describe_exclusions_2_grouped_R}
exclusion_tbl <- aah_summary_all |>
  filter(handedness == "Right") |>
  rename(exclude_any = exclude_any) |>
summarize(across(starts_with("exclude"), sum)) |>
pivot_longer(cols = everything(),
             names_to = 'exclusion', values_to = "n",
             names_prefix = "exclude_") |>
  mutate('exclusion' = recode(exclusion,
    any = "Any",
    country = "Non-US country",
    age = "Age outside 18-40",
    done_before = "Reported having done the task before",
    high_rt = "Navon: High RT (median > 1500ms)",
    low_rt = "Navon: Low RT (median < 200ms)",
    low_acc = "Navon: Low accuracy (below 60% on any block)",
    many_gos = "Navon: Too many 'gos' (78/80 trials or more)",
    no_ehi = "Quit before completing EHI",
    ehi_mismatch = "Prescreener/EHI mismatch",
    headphone_check = "Failed headphone check (<5/6)",
    stereo_check = "Failed stereo check (<5/6)",
    DL_mono_acc = "Dichotic listening: low mono accuracy (<75%)",
    DL_dual_acc = "Dichotic listening: low dual accuracy (<60%)"
  )) |>
  arrange(-n, exclusion) |>
  select(n, exclusion) |>
  rename('Reason for exclusion' = exclusion,
         "n (Right)" = n)

exclusion_tbl |> pretty_table()
```
<br>
Mixed handers (n = `r n_ehi_mixed`)
```{r describe_exclusions_2_grouped_M}
exclusion_tbl <- aah_summary_all |>
  filter(handedness == "Mixed") |>
  rename(exclude_any = exclude_any) |>
summarize(across(starts_with("exclude"), sum)) |>
pivot_longer(cols = everything(),
             names_to = 'exclusion', values_to = "n",
             names_prefix = "exclude_") |>
  mutate('exclusion' = recode(exclusion,
    any = "Any",
    country = "Non-US country",
    age = "Age outside 18-40",
    done_before = "Reported having done the task before",
    high_rt = "Navon: High RT (median > 1500ms)",
    low_rt = "Navon: Low RT (median < 200ms)",
    low_acc = "Navon: Low accuracy (below 60% on any block)",
    many_gos = "Navon: Too many 'gos' (78/80 trials or more)",
    no_ehi = "Quit before completing EHI",
    ehi_mismatch = "Prescreener/EHI mismatch",
    headphone_check = "Failed headphone check (<5/6)",
    stereo_check = "Failed stereo check (<5/6)",
    DL_mono_acc = "Dichotic listening: low mono accuracy (<75%)",
    DL_dual_acc = "Dichotic listening: low dual accuracy (<60%)"
  )) |>
  arrange(-n, exclusion) |>
  select(n, exclusion) |>
  rename('Reason for exclusion' = exclusion,
         "n (Mixed)" = n)

exclusion_tbl |> pretty_table()
```
<br>
Left handers (n = `r n_ehi_left`)
```{r describe_exclusions_2_grouped_L}
exclusion_tbl <- aah_summary_all |>
  filter(handedness == "Left") |>
  rename(exclude_any = exclude_any) |>
summarize(across(starts_with("exclude"), sum)) |>
pivot_longer(cols = everything(),
             names_to = 'exclusion', values_to = "n",
             names_prefix = "exclude_") |>
  mutate('exclusion' = recode(exclusion,
    any = "Any",
    country = "Non-US country",
    age = "Age outside 18-40",
    done_before = "Reported having done the task before",
    high_rt = "Navon: High RT (median > 1500ms)",
    low_rt = "Navon: Low RT (median < 200ms)",
    low_acc = "Navon: Low accuracy (below 60% on any block)",
    many_gos = "Navon: Too many 'gos' (78/80 trials or more)",
    no_ehi = "Quit before completing EHI",
    ehi_mismatch = "Prescreener/EHI mismatch",
    headphone_check = "Failed headphone check (<5/6)",
    stereo_check = "Failed stereo check (<5/6)",
    DL_mono_acc = "Dichotic listening: low mono accuracy (<75%)",
    DL_dual_acc = "Dichotic listening: low dual accuracy (<60%)"
  )) |>
  arrange(-n, exclusion) |>
  select(n, exclusion) |>
  rename('Reason for exclusion' = exclusion,
         "n (Left)" = n)

exclusion_tbl |> pretty_table()
```
<br>



### Demographics (Keepers) {.tabset .tabset-pills}


#### Navon + DL

<br>
Demographics for included participants, by handedness group (EHI bins). 
```{r}
hand_demo_summary_table(aah_summary) |> 
  pretty_table() |>
  tab_footnote("Left: (EHI <= -40)  |  Mixed: (-40 < EHI < 40)  |  Right: (EHI >= 40)")
```
<br>

```{r ehi_bin_handedness_plot_keepers}
## Show distribution of handedness by EHI bin
plot_color = plot_blue

h_data_n <-
  aah_summary |>
  group_by(handedness) |>
  summarize(n = str_c("n = ", as.character(n())))

fig_path <- here(fig_dir, "bin_ehi_keepers_any.png")

if (use_cached_demofigs == FALSE) {
  g <- ggplot(aah_summary, aes(x = ehi)) +
    geom_histogram(
      color = NA,
      fill = plot_color,
      alpha = .8,
      binwidth = 8,
      boundary = 100
    ) +
    labs(x = "EHI") +
    xlim(c(-104, 104)) +
    facet_grid( ~ handedness) +
    geom_text(
      data = h_data_n,
      aes(x = -100, y = 5, label = n),
      hjust = 0,
      colour = "gray20",
      inherit.aes = FALSE,
      parse = FALSE
    ) +
    labs(title = "Distribution within each EHI bin (keepers only)")
  
  g <- g |> gg_style() + theme(aspect.ratio = 1 / 1,
                                    axis.title.y = element_blank())
  
  ggsave(fig_path, g, "png", height = 3, width = 6)
}

include_graphics(fig_path)
```

Demographics for all included participants.

```{r demographics_summary_included}
rt_demo <- demo_summary_table(aah_summary)
rt_demo |> 
  pretty_table() |> tab_header(title = "Demographics", subtitle = "Summary")
```
<br>
```{r country_included}
demo_country_table(aah_summary) |> 
  pretty_table()
```
<br>
```{r race_included}
demo_race_table(aah_summary) |> 
 pretty_table()
```
<br>
```{r ethnicity_included}
demo_ethnicity_table(aah_summary) |> 
 pretty_table()
```
<br>

#### Navon

<br>
Demographics for included participants, by handedness group (EHI bins). 
```{r}
hand_demo_summary_table(aah_summary_navon) |> 
  pretty_table() |>
  tab_footnote("Left: (EHI <= -40)  |  Mixed: (-40 < EHI < 40)  |  Right: (EHI >= 40)")
```
<br>

```{r ehi_bin_handedness_plot_keepers_navon}
## Show distribution of handedness by EHI bin
plot_color = plot_blue

h_data_n <-
  aah_summary_navon |>
  group_by(handedness) |>
  summarize(n = str_c("n = ", as.character(n())))

fig_path <- here(fig_dir, "bin_ehi_keepers_navon.png")

if (use_cached_demofigs == FALSE) {
  g <- ggplot(aah_summary_navon, aes(x = ehi)) +
    geom_histogram(
      color = NA,
      fill = plot_color,
      alpha = .8,
      binwidth = 8,
      boundary = 100
    ) +
    labs(x = "EHI") +
    xlim(c(-104, 104)) +
    facet_grid( ~ handedness) +
    geom_text(
      data = h_data_n,
      aes(x = -100, y = 5, label = n),
      hjust = 0,
      colour = "gray20",
      inherit.aes = FALSE,
      parse = FALSE
    ) +
    labs(title = "Distribution within each EHI bin (keepers only)")
  
  g <- g |> gg_style() + theme(aspect.ratio = 1 / 1,
                                    axis.title.y = element_blank())
  
  ggsave(fig_path, g, "png", height = 3, width = 6)
}

include_graphics(fig_path)
```

Demographics for all included participants.

```{r demographics_summary_included_navon}
rt_demo <- demo_summary_table(aah_summary_navon)
rt_demo |> 
  pretty_table() |> tab_header(title = "Demographics", subtitle = "Summary")
```
<br>
```{r country_included_navon}
demo_country_table(aah_summary_navon) |> 
  pretty_table()
```
<br>
```{r race_included_navon}
demo_race_table(aah_summary_navon) |> 
 pretty_table()
```
<br>
```{r ethnicity_included_navon}
demo_ethnicity_table(aah_summary_navon) |> 
 pretty_table()
```
<br>

#### Dichotic Listening

<br>
Demographics for included participants, by handedness group (EHI bins). 
```{r}
hand_demo_summary_table(aah_summary_dl) |> 
  pretty_table() |>
  tab_footnote("Left: (EHI <= -40)  |  Mixed: (-40 < EHI < 40)  |  Right: (EHI >= 40)")
```
<br>

```{r ehi_bin_handedness_plot_keepers_dl}
## Show distribution of handedness by EHI bin
plot_color = plot_blue

h_data_n <-
  aah_summary_dl |>
  group_by(handedness) |>
  summarize(n = str_c("n = ", as.character(n())))

fig_path <- here(fig_dir, "bin_ehi_keepers_dl.png")

if (use_cached_demofigs == FALSE) {
  g <- ggplot(aah_summary_dl, aes(x = ehi)) +
    geom_histogram(
      color = NA,
      fill = plot_color,
      alpha = .8,
      binwidth = 8,
      boundary = 100
    ) +
    labs(x = "EHI") +
    xlim(c(-104, 104)) +
    facet_grid( ~ handedness) +
    geom_text(
      data = h_data_n,
      aes(x = -100, y = 5, label = n),
      hjust = 0,
      colour = "gray20",
      inherit.aes = FALSE,
      parse = FALSE
    ) +
    labs(title = "Distribution within each EHI bin (keepers only)")
  
  g <- g |> gg_style() + theme(aspect.ratio = 1 / 1,
                                    axis.title.y = element_blank())
  
  ggsave(fig_path, g, "png", height = 3, width = 6)
}

include_graphics(fig_path)
```

```{r demographics_summary_included_dl}
rt_demo <- demo_summary_table(aah_summary_dl)
rt_demo |> 
  pretty_table() |> tab_header(title = "Demographics", subtitle = "Summary")
```
<br>
```{r country_included_dl}
demo_country_table(aah_summary_dl) |> 
  pretty_table()
```
<br>
```{r race_included_dl}
demo_race_table(aah_summary_dl) |> 
 pretty_table()
```
<br>
```{r ethnicity_included_dl}
demo_ethnicity_table(aah_summary_dl) |> 
 pretty_table()
```
<br>

#### Group differences?

Any demographics differences between handedness groups?

<br>
```{r}
lm(data = aah_summary, formula = age ~ handedness) |> 
  emmeans(~ handedness) |> 
  contrast("pairwise") |> 
  summary(infer = T, adj = "none") |>
  as_tibble() |> 
  pretty_table("Age (years)")
```
<br>
```{r}
lm(data = aah_summary, formula = education ~ handedness) |> 
  emmeans(~ handedness) |> 
  contrast("pairwise") |> 
  summary(infer = T, adj = "none") |>
  as_tibble() |> 
  pretty_table("Education (years)")
```
<br>
```{r}
sex_data <- aah_summary |> filter(sex %in% c("Male", "Female")) |> 
  mutate(sex = as.factor(sex))

glm(data = sex_data,
    formula = sex ~ handedness,
    family = "binomial") |> 
  emmeans(~ handedness) |>
  contrast("pairwise") |>
  summary(infer = T, adj = "none", type = "response") |>
  as_tibble() |>
  pretty_table("Sex") |> 
  tab_footnote(footnote = "Odds (female / male)",
               locations = cells_column_labels(columns = "odds.ratio"))
```




