---
title: "Experiment 1: Accuracy Analyses"
pagetitle: "exp 1 | accuracy analyses"
author: "Owen Morgan"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---

<style type="text/css">
  body{
  font-family: Avenir;
  font-size: 12pt;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      fig.align = "center", fig.width = 9,
                      fig.height = 6, results = "asis")
options(knitr.kable.NA = "")

cli.progress_show_after <- 0

## Do not use scientific notation until 9 decimal places.
options(scipen = 9, digits = 9)

# Suppress summarise info
options(dplyr.summarise.inform = FALSE)
```

```{r lib}
library(here)
library(tidyverse)
library(cli) # For printing error messages

library(lme4)
library(emmeans)
library(broom)
library(gt)

library(ggpubr) ## functions for plotting SD, SEM, CI.
library(ggbeeswarm)
library(patchwork)
library(ggh4x) ## for nested facets

library(knitr) # For include_graphics

source(here::here("lib", "util.R"))
source(here::here("lib", "demographics.R"))
source(here::here("lib", "plots-jepg.R"))

EXPERIMENT_DIR <- "experiment_1"
source(here::here(EXPERIMENT_DIR, "lib", "load_process", "load_process.R"))

## Colors for plots
plot_blue <- c("#337aB7")
plot_colors <- c("#4477AA",
                 "#EE6677",
                 "#CCBB44",
                 "#66CCEE",
                 "#AA3377",
                 "#228833",
                 "#BBBBBB")
```

```{r config}
proc_dir <- set_or_make_dir(label = "proc",
  here::here(EXPERIMENT_DIR, "data", "proc_exp_n1008")
)
fig_dir <- set_or_make_dir(label = "fig",
  here::here(EXPERIMENT_DIR, "figures")
)
manual_cache_dir <- set_or_make_dir(label = "manual cache",
 here::here(EXPERIMENT_DIR, "manual_cache", "exp_n1008")
)

experiment_label <- "Experiment 1"

## Emmeans settings (use Satterthwaire approx. instead of default t-to-z for large df)
## See: Luke (2017). Evaluating significance in linear mixed-effects models in R
DF_METHOD <- "satterthwaite"
LMERTEST_LIMIT <- 500000

## Figure settings
DEFAULT_HEIGHT = 3
DEFAULT_WIDTH = 5

use_cached_models <- T
use_cached_figs <- T
use_cached_proc_data <- T
```

# {.tabset}
```{r load_data}
## Load "the data" with all subjects & trials.
aah_long <- load_aah_long(proc_dir)

## Load summary data table (for quick demographic analyses)
## with all subjects.
aah_summary_all <- load_aah_summary(proc_dir)
```

```{r prepare_data}
#### PREPARE SUMMARY DATA FOR DEMOGRAPHICS ANALYSES (NAVON EXCLUSIONS)
if (use_cached_proc_data == FALSE) {
cli::cli_alert_info("Filtering summary data for analysis (no excluded subjects).")
cli::cli_bullets(c(" " = "aah_summary_all -> aah_summary"))
aah_summary <- aah_summary_all |>
    filter(exclude == 0) |>
    select(-starts_with("exclude")) |> 
  mutate(
    handedness_extremes = case_when(ehi == -100 ~ "Left",
                                    ehi == 100 ~ "Right",
                                    ehi > -100 & ehi < 100 ~ "Mixed")
  )
  saveRDS(aah_summary, here(manual_cache_dir, "aah_summary.rds"))
} else {
  aah_summary <- readRDS(here(manual_cache_dir, "aah_summary.rds"))
}

#### PREPARE TRIAL-LEVEL DATA FOR RT, ACCURACY ANALYSES
## Prepare "the data" (aah_long) for all analyses:
## Filter out practice trials, absent trials, and excluded subjects
## This data (all present trials, correct or incorrect) will be used for
## accuracy analyses
if (use_cached_proc_data == FALSE) {
cli::cli_alert_info("Filtering long navon data for analysis (no excluded subjects; experimental trials (not practice) only; target present only).")
aah <- aah_long |>
  filter(exclude == 0) |>
  filter(block_type == "main" & target_present == "yes") |>
  select(-starts_with("exclude")) |>
  ## Recode "level", "target" for nicer printing.
  mutate(level = recode(level, global = "Global", local = "Local")) |>
  mutate(target = recode(target, square = "Square", rectangle = "Rectangle")) |>
  ## Code handedness extremes
  mutate(
    handedness_extremes = case_when(ehi == -100 ~ "Left",
                                    ehi == 100 ~ "Right",
                                    ehi > -100 & ehi < 100 ~ "Mixed")
    )
  saveRDS(aah, here(manual_cache_dir, "aah.rds"))
} else {
  aah <- readRDS(here(manual_cache_dir, "aah.rds"))
}

## For RT analyses, prepare dataset with only correct, present trials.
## In our RT model, we only care about correct responses to present trials.
if (use_cached_proc_data == FALSE) {
aah_correct <- aah |> filter(correct == T)
  saveRDS(aah_correct, here(manual_cache_dir, "aah_correct.rds"))
} else {
  aah_correct <- readRDS(here(manual_cache_dir, "aah_correct.rds"))
}

## Relevel field and level with RVF first (unintuitive for plotting),
## so that emmeans will show a positive number for LVF global bias.
if (use_cached_proc_data == FALSE) {
aah_for_rt_model <- aah_correct |>
  mutate(level = level |> factor(levels = c("Global", "Local")),
         field = field |> factor(levels = c("RVF", "LVF")))
  saveRDS(aah_for_rt_model, here(manual_cache_dir, "aah_for_rt_model.rds"))
} else {
  aah_for_rt_model <- readRDS(here(manual_cache_dir, "aah_for_rt_model.rds"))
}

## For accuracy analyses, prepare dataset will all present trials.
## Relevel field and level,
## so that emmeans will show a positive number for LVF global bias.
if (use_cached_proc_data == FALSE) {
aah_for_acc_model <- aah |>
  mutate(level = level |> factor(levels = c("Global", "Local")),
         field = field |> factor(levels = c("RVF", "LVF")))
  saveRDS(aah_for_acc_model, here(manual_cache_dir, "aah_for_acc_model.rds"))
} else {
  aah_for_acc_model <- readRDS(here(manual_cache_dir, "aah_for_acc_model.rds"))
}

#### PREPARE SUBJECT_LEVEL DATA FOR RT, ACCURACY ANALYSES
## Prepare subject-level data (RT)
if (use_cached_proc_data == FALSE) {
rt_subject <- aah_correct |> group_by(subject, field, level, handedness) |>
  summarize(rt = median(rt))
  saveRDS(rt_subject, here(manual_cache_dir, "rt_subject.rds"))
} else {
  rt_subject <- readRDS(here(manual_cache_dir, "rt_subject.rds"))
}


## Prepare subject-level LVF Global bias summary (RT)
if (use_cached_proc_data == FALSE) {
rt_1 <- rt_subject |>
  pivot_wider(names_from = c(field, level),
              values_from = rt) |>
  mutate(LVF_Global_Bias = (RVF_Global - RVF_Local) - (LVF_Global - LVF_Local)) |>
  mutate(all_one_group = "all_one_group")
  saveRDS(rt_1, here(manual_cache_dir, "rt_1.rds"))
} else {
  rt_1 <- readRDS(here(manual_cache_dir, "rt_1.rds"))
}

## Prepare subject-level LVF Global bias summary (Accuracy)
## (For accuracy, include incorrect trials!)
if (use_cached_proc_data == FALSE) {
acc_subject <- aah |> group_by(subject, field, level, handedness, sample, sample2) |>
  summarize(
    total_responses = n(),
    n_present_resp = sum(correct),
    n_absent_resp = total_responses - n_present_resp,
    n_correct = sum(correct),
    acc = 100 * (n_correct / total_responses)
  ) |>
  select(subject, field, level, acc, handedness, sample, sample2) |>
  mutate(level = recode(level, global = "Global", local = "Local"))
  saveRDS(acc_subject, here(manual_cache_dir, "acc_subject.rds"))
} else {
  acc_subject <- readRDS(here(manual_cache_dir, "acc_subject.rds"))
}

if (use_cached_proc_data == FALSE) {
acc_1 <- acc_subject |>
  pivot_wider(names_from = c(field, level),
              values_from = acc) |>
  mutate(LVF_Global_Bias = (LVF_Global - LVF_Local) - (RVF_Global - RVF_Local)) |>
  mutate(all_one_group = "all_one_group")
  saveRDS(acc_1, here(manual_cache_dir, "acc_1.rds"))
} else {
  acc_1 <- readRDS(here(manual_cache_dir, "acc_1.rds"))
}
```

## Demographics {.tabset .tabset-pills}

Demographics for all included participants.
<br>
```{r demo_summary}
rt_demo <- demo_summary_table(aah_summary)
rt_demo |> pretty_table() |> tab_header(title = "Demographics", subtitle = "Summary")
```
<br>

```{r}
hand_demo_summary_table(aah_summary) |> pretty_table() |>
  tab_footnote("Left: (EHI <= -40)  |  Mixed: (-40 < EHI < 40)  |  Right: (EHI >= 40)")
```
<br>
```{r ehi_distribution_plot_purple1}
middle_purple1 <- "#996F91" ## In between plot colors one and two
fig_path_var <- here(fig_dir, "demo_ehi_dots_purple.png")

if (use_cached_figs == F) {
  ehi_plot_data <- aah_summary |> group_by(ehi) |> summarize(n = n())
  g <- gg_ehi_dotarea(ehi_plot_data, plot_color = middle_purple1,
                      cutoff = 40, cutoff_label_ypos = 120)
  ggsave(fig_path_var, g, "png", height = 3, width = 6)
}

include_graphics(fig_path_var)
```



## Categorical handedness (secondary)
```{r}
## Relevel so that emmeans shows a positive number for greater effect in RVF, local.
aah_for_acc_model <- aah_for_acc_model |>
  mutate(handedness = handedness |> factor(levels = c("Right", "Mixed", "Left")),
         field = field |> factor(levels = c("RVF", "LVF")),
         level = level |> factor(levels = c("Local", "Global")))


## Switch level, not field.
## Field: RVF, LVF (original)
## Handedness: Right, Left (switched)
## Level: Local, Global (switched)
```


### Summary

For accuracy, we observed no significant interaction of field by level by handedness (\textit{OR} = 1.11, 95\% CI [0.86, 1.44], $\chi^2(1)$ = 0.65, \textit{p} = .42, two-sided). Both groups showed LVF global>local bias: the relative odds of correct/incorrect responses for local/global, RVF/LVF stimuli for right handers was 1.76 (95\% CI [1.49, 2.09], \textit{z} = 6.48, \textit{p} < .0001, one-sided); for left handers, 1.96 (95\% CI [1.63, 2.37], \textit{p} < .0001, two-sided).

Within the local level, left handers' hemifield bias did not differ significantly from right handers' (OR = 1.04, 95\% CI [0.89, 1.21], \textit{z} = 0.44, \textit{p} = .66, two-sided). Right handers showed showed significant RVF bias (\textit{OR} = 1.16, 95\% CI [1.04, 1.29], z = 2.66, \textit{p} = .008, two-sided), and left handers showed marginal RVF bias (\textit{OR} = 1.12, 95\% CI [1.00, 1.25], \textit{z} = 1.96, \textit{p} = .050, two-sided).

### Stats

Accuracy is modeled as a binomial effect of field, level, and handedness, using binary correct/incorrect data from every target-present trial:
<br>
<br>
`glmer( correct ~ field*level*handedness + (1 | subject), family = "binomial" )`
<br>
<br>
```{r acc_model_2bins}
#### FxLxH (prepare model)
## Make a binomial logistic model using data from every trial.
if (use_cached_models == FALSE) {
  ## Make a model with two handedness bins: Right and Left
  aah_for_acc_model_2bins <-
    aah_for_acc_model |> filter(handedness %in% c("Right", "Left"))
  
  acc_model_2bins <-
    glmer(correct ~ field * level * handedness + (1 | subject),
          data = aah_for_acc_model_2bins,
          family = "binomial")
  
  ## Create emmeans model object, and manually cache it.
  acc_emm_2bins <-
    emmeans(acc_model_2bins, ~ field * level * handedness)
  
  ## Manually cache model
  saveRDS(acc_model_2bins,
          here(manual_cache_dir,
               "acc_model_2bins.rds"))
  saveRDS(acc_emm_2bins, here(manual_cache_dir, "acc_emm_2bins.rds"))
  
} else if (use_cached_models == TRUE) {
  ## Load cached model
  acc_model_2bins <- readRDS(here(manual_cache_dir, "acc_model_2bins.rds"))
  acc_emm_2bins <- readRDS(here(manual_cache_dir, "acc_emm_2bins.rds"))
}
```

<br>
```{r acc_interaction_anova}
### FxLxH (Likelihood ratio test)
## Use anova() on competing models to test 2-way interaction.
if (use_cached_models == FALSE) {
  ## Create and manually cache ANOVA
  acc_model_no_interaction <-
    update(acc_model_2bins, . ~ . - field:level:handedness)
  
  interaction_anova <-
    interaction_stats(acc_model_2bins, acc_model_no_interaction)
  
  ## Manually cache model
  saveRDS(acc_model_no_interaction, here(manual_cache_dir,
                                "acc_model_no_interaction_2bins.rds"))
  saveRDS(interaction_anova, here(manual_cache_dir,
                                "acc_anova_2bins.rds"))
  
} else if (use_cached_models == TRUE) {
  ## Load cached ANOVA
  acc_model_no_interaction <- readRDS(here(manual_cache_dir, "acc_model_no_interaction_2bins.rds"))
  interaction_anova <- readRDS(here(manual_cache_dir, "acc_anova_2bins.rds"))
}

interaction_anova |>
  as_tibble() |>
  rename(p.value = `Pr(>Chisq)`) |> 
  format_p.value() |> 
  pretty_table() |> 
  tab_header(title = str_glue("{experiment_label}: Field by Level by Handedness (Accuracy)"), 
             subtitle = "ANOVA: compare models with vs. without interaction term") |> 
  tab_footnote(footnote = "F-test (two-sided? https://daniellakens.blogspot.com/2016/04/one-sided-f-tests-and-halving-p-values.html)",
               locations = cells_column_labels(columns = p.value))
```
<br>
```{r acc_interaction_emm}
### FxLxH
## Use emmeans() to test 3-way interaction.
acc_interaction_emm <- acc_emm_2bins |> 
  contrast(interaction = c("consec")) |>
  summary(infer = T, type = "response")

acc_interaction_emm |>
  as_tibble() |>
  format_p.value() |> 
  pretty_table() |>
  tab_header(title = str_glue("{experiment_label}: Field by Level by Handedness (Accuracy)"),
             subtitle = "Compare effect estimate to zero with emmeans()") |>
  tab_footnote(footnote =  "Backtransformed to odds ratio from log odds ratio (tests are performed on log odds ratio scale). A ratio < 1 means local bias is stronger in the RVF for right handers (predicted by AAH)",
               locations = cells_column_labels(columns = odds.ratio)) |>
  tab_footnote(footnote = "'Inf' df is expected when emmeans does logistic regression. See emmeans FAQ: https://cran.r-project.org/web/packages/emmeans/vignettes/FAQs.html#asymp.",
               locations = cells_column_labels(columns = df)) |>
  tab_footnote(footnote = "Confidence level: 95%",
               locations = cells_column_labels(columns = ends_with("CL"))) |>
  tab_footnote(footnote = "Two-sided",
               locations = cells_column_labels(columns = p.value))
```
<br>
```{r acc_handedness_bias}
#### FxL | H
## Estimate the effect of field by level for each handedness group
acc_emm2 <- emmeans(acc_model_2bins, ~field*level | handedness) |>
  contrast(interaction = "consec") |>
  summary(infer = T, adj = "none", type = "response")

acc_emm2 |>
  as_tibble() |>
  format_p.value() |>
  pretty_table() |>
  tab_header(title = str_glue("{experiment_label}: Field by Level (by Handedness) (Accuracy)"),
             subtitle = "Compare effect estimate to zero with emmeans()") |>
  tab_footnote(footnote =  "Backtransformed to odds ratio from log odds ratio (tests are performed on log odds ratio scale). A ratio < 1 means global bias is stronger in the LVF, as predicted for right handers.",
               locations = cells_column_labels(columns = odds.ratio)) |>
  tab_footnote(footnote = "'Inf' df is expected when emmeans does logistic regression. See emmeans FAQ: https://cran.r-project.org/web/packages/emmeans/vignettes/FAQs.html#asymp.",
               locations = cells_column_labels(columns = df)) |>
  tab_footnote(footnote = "Confidence level: 95%",
               locations = cells_column_labels(columns = ends_with("CL"))) |>
  tab_footnote(footnote = "Two-sided",
               locations = cells_column_labels(columns = p.value))
```
<br>
```{r}
#### FxH | L
## Estimate the effect of field by handedness, for each level.
acc_emm2 <- emmeans(acc_model_2bins, ~field*handedness | level) |>
  contrast(interaction = "consec") |>
  summary(infer = T, adj = "none", type = "response")

acc_emm2 |>
  as_tibble() |>
  format_p.value() |>
  pretty_table() |>
  tab_header(title = str_glue("{experiment_label}: Field by Handedness (by Level) (Accuracy)"),
             subtitle = "Compare effect estimate to zero with emmeans()") |>
  tab_footnote(footnote =  "Backtransformed to odds ratio from log odds ratio (tests are performed on log odds ratio scale). A ratio < 1 means global bias is stronger in the LVF, as predicted for right handers.",
               locations = cells_column_labels(columns = odds.ratio)) |>
  tab_footnote(footnote = "'Inf' df is expected when emmeans does logistic regression. See emmeans FAQ: https://cran.r-project.org/web/packages/emmeans/vignettes/FAQs.html#asymp.",
               locations = cells_column_labels(columns = df)) |>
  tab_footnote(footnote = "Confidence level: 95%",
               locations = cells_column_labels(columns = ends_with("CL"))) |>
  tab_footnote(footnote = "Two-sided",
               locations = cells_column_labels(columns = p.value))
```
<br>
```{r acc_handedness_bias_bylevel}

#### F | L | H
## Estimate the effect of field by level for each handedness group
acc_emm2 <- emmeans(acc_model_2bins, ~field | handedness + level) |>
  contrast("pairwise", by = c("handedness", "level")) |>
  summary(infer = T, adj = "none", type = "response")

acc_emm2 |>
  as_tibble() |>
  format_p.value() |>
  arrange(handedness, level) |> 
  pretty_table() |>
  tab_header(title = str_glue("{experiment_label}: Hemifield bias (by Level, by Handedness) (Accuracy)"),
             subtitle = "Compare effect estimate to zero with emmeans()") |>
  tab_footnote(footnote =  "Backtransformed to odds ratio from log odds ratio (tests are performed on log odds ratio scale). A ratio > 1 means RVF bias.",
               locations = cells_column_labels(columns = odds.ratio)) |>
  tab_footnote(footnote = "'Inf' df is expected when emmeans does logistic regression. See emmeans FAQ: https://cran.r-project.org/web/packages/emmeans/vignettes/FAQs.html#asymp.",
               locations = cells_column_labels(columns = df)) |>
  tab_footnote(footnote = "Confidence level: 95%",
               locations = cells_column_labels(columns = ends_with("CL"))) |>
  tab_footnote(footnote = "Two-sided",
               locations = cells_column_labels(columns = p.value))
```
<br>

## Continuous handedness (secondary)

### Summary

For accuracy, we find no significant interaction of field by level by EHI (Beta = 0.0002 logodds per EHI unit, 95% CI [-0.001, 0.002], p = .40, one-sided). Estimated LVF global bias hardly differs for strong left handers (EHI -100: OR = 1.67, 95% CI [1.37, 2.03]) and strong right handers (EHI +100: OR = 1.73, 95% CI [1.45, 2.07]).

### Stats

Model accuracy as a binomial effect of field, level, and EHI (continuous):
<br>
<br>
`acc_ehi_model <- glmer( correct ~ field*level*ehi + (1 | subject), family = "binomial" )`
<br>
<br>
```{r acc_model_ehil}
## Prepare data, so emmeans contrasts show
## Global bias as a positive number.
aah_for_acc_ehi_model <- aah_for_acc_model |>
  mutate(level = level |> factor(levels = c("Global", "Local")),
         field = field |> factor(levels = c("LVF", "RVF")))
```

```{r acc_model_ehi2}
## Make a binomial logistic model using data from every trial.
if (use_cached_models == FALSE) {
  
  ## Create and cache binomial model
  acc_model_ehi <-
    glmer(correct ~ field * level * ehi + (1 | subject),
          data = aah_for_acc_ehi_model,
          family = "binomial")
 
  ## Create emmeans model object, and manually cache it.
  acc_emm_ehi <-
    emmeans(acc_model_ehi, ~ field * level * ehi)
  
  ## Manually cache model
  saveRDS(acc_model_ehi, here(manual_cache_dir,
                              "acc_model_ehi.rds"))
  saveRDS(acc_emm_ehi, here(manual_cache_dir, "acc_emm_ehi.rds"))
  
} else if (use_cached_models == TRUE) {
  ## Load cached model
  acc_model_ehi <- readRDS(here(manual_cache_dir, "acc_model_ehi.rds"))
  acc_emm_ehi <- readRDS(here(manual_cache_dir, "acc_emm_ehi.rds"))
}
```
<br>
```{r acc_interaction_anova_ehi}
## Use anova() on competing models to test 2-way interaction.

if (use_cached_models == FALSE) {
  ## Create and manually cache ANOVA
  acc_model_no_interaction <-
    update(acc_model_ehi, . ~ . - field:level:ehi)
  
  interaction_anova <-
    interaction_stats(acc_model_ehi, acc_model_no_interaction)
  
  ## Manually cache model
  saveRDS(interaction_anova,
          here(manual_cache_dir,
               "acc_anova_ehi.rds"))
  
} else if (use_cached_models == TRUE) {
  ## Load cached ANOVA
  interaction_anova <- readRDS(here(manual_cache_dir, "acc_anova_ehi.rds"))
}

interaction_anova |>
  as_tibble() |>
  rename(p.value = `Pr(>Chisq)`) |> 
  format_p.value() |> 
  pretty_table() |> 
  tab_header(title = "Field by level by EHI interaction (Accuracy)", 
             subtitle = "ANOVA: compare models with vs. without interaction term") |> 
  tab_footnote(footnote = "F-test (two-sided? https://daniellakens.blogspot.com/2016/04/one-sided-f-tests-and-halving-p-values.html)",
               locations = cells_column_labels(columns = p.value))
```
<br>
```{r}
## Test whether interaction slope differs from zero, with emmeans

## This code estimates the effect of EHI on acc for each field*level:
acc_emt <- emtrends(acc_model_ehi, pairwise ~ field*level, var = "ehi")
## We want to compare the effect of EHI on acc for:
## (LVF Global - LVF Local) - (RVF Global - RVF Local)

## Report interaction estimate, with CI and p value.
acc_emt[[1]] |> contrast(interaction = c("consec"), var = "ehi") |> 
  summary(infer = T)|>
  format_p.value() |> 
  pretty_table(digits = 4) |> 
  tab_header(title = "Field by level by EHI interaction (Accuracy)",
             subtitle = "Compare effect estimate to zero with emmeans()") |>
  tab_footnote(footnote = "A positive number means global bias is stronger in LVF for right handers (as predicted), in logodds per EHI unit (-100 to 100). Multiply this value by 200 to get the estimated difference in LVF global bias for strong left vs. right handers.",
               locations = cells_column_labels(columns = estimate)) |>
  tab_footnote(footnote = "Two-sided",
               locations = cells_column_labels(columns = p.value)) |>
  tab_footnote(footnote = "Confidence level: 95% (two-sided)",
               locations = cells_column_labels(columns = ends_with("CL")))
```
<br>
```{r}
## Report EHI effect on bias by field, with CI and p-value
acc_emt$contrasts |>
  summary(infer = T, adj = "none") |> 
  as_tibble() |> 
  filter(contrast %in%
           c("LVF Global - LVF Local", "RVF Global - RVF Local")) |> 
  format_p.value() |> 
  pretty_table(digits = 4) |> 
  tab_header(title = "Field by level interaction (Accuracy)") |>
  tab_footnote(footnote = "A positive number means more global bias, in logodds per EHI unit (-100 to 100)",
               locations = cells_column_labels(columns = estimate)) |>
  tab_footnote(footnote = "Two-sided, uncorrected",
               locations = cells_column_labels(columns = p.value)) |>
  tab_footnote(footnote = "Confidence level: 95%",
               locations = cells_column_labels(columns = ends_with("CL"))) |>
  tab_footnote(footnote = "Z-approximation",
               locations = cells_column_labels(columns = df))
```
<br>
```{r}
## Report EHI effect by field and level, with CI and p-value
acc_emt$emtrends |> summary(infer = T, adj = "none") |>
  as_tibble() |>
  format_p.value() |>
  pretty_table(digits = 4) |>
  tab_header(title = "Slope of EHI and Accuracy by field and level",
             subtitle = "Compare effect estimate to zero with emmeans()") |>
  tab_footnote(footnote = "A positive number means higher accuracy for right handers, in logodds per EHI unit (-100 to 100).",
               locations = cells_column_labels(columns = ehi.trend)) |>
  tab_footnote(footnote = "Two-sided",
               locations = cells_column_labels(columns = p.value)) |>
  tab_footnote(footnote = "Confidence level: 95%",
               locations = cells_column_labels(columns = ends_with("CL"))) |>
  tab_footnote(footnote = "Z-approximation",
               locations = cells_column_labels(columns = df))
```
<br>

---

<br>
```{r}
## LVF Global bias by handedness.
## Pull estimates for strong left and right handers (ehi = -100, +100)
## Estimate effect of ehi on field x level.

## Use ref_grid (following quant 2 HW5)
ref <- ref_grid(acc_model_ehi, at = list(ehi = c(-100, 0, 100)))


## Show estimates for left and right handers.
ref |>
  contrast(interaction = c("consec"), by = "ehi") |>
  summary(infer = T, type = "response") |>
  as_tibble() |> 
  format_p.value() |> 
  pretty_table() |> 
  tab_header(title = "Estimated LVF global bias, by EHI score") |> 
  tab_footnote(footnote = "Strong left hander: -100; Mixed hander: 0; Strong right hander: +100",
               locations = cells_column_labels(columns = ehi)) |> 
  tab_footnote(footnote = "Estimated LVF global bias. An odds ratio > 1 means LVF global bias.",
               locations = cells_column_labels(columns = odds.ratio))
```
<br>
```{r}
## Global bias by field, by handedness.
ref |>
  contrast("pairwise", by = "ehi") |> 
  summary(infer = T, type = "response") |> 
  as_tibble() |> 
  slice(2, 5, 8, 11, 14, 17) |> 
  format_p.value() |> 
  arrange(ehi) |> 
  pretty_table() |> 
  tab_header(title = "Estimated global bias by field, by EHI score") |> 
  tab_footnote(footnote = "Estimated global bias. An odds ratio > 1 means global bias.",
               locations = cells_column_labels(columns = odds.ratio))
```
<br>
```{r}
## Accuracy by field and level, by handedness.
ref |>
  summary(infer = T, type = "response") |> 
  as_tibble() |> 
  select(field, level, ehi, prob, ends_with("CL")) |> 
  pretty_table() |> 
  tab_header(title = "Accurracy by field and level, by EHI score") |> 
  tab_footnote(footnote = "Accuracy (% correct)",
               locations = cells_column_labels(columns = prob))
```
<br>


$$
log(1.73) = .548
$$
$$
log(1.67) = .513
$$
$$
log(1.73) - log(1.67) = .0353
$$
$$
.0353 / 200 = -0.000185 logodds / EHI unit
$$
<br> 

The model estimates that a strong right hander (EHI +100) will have 1.73/1.67 = 1.04 greater odds of correctness for LVF global stimuli versus a strong left hander (EHI -100). Each unit change in EHI (-100:100) corresponds to a **0.0002** (logodds) difference in LVF global bias. This matches the slope estimate given by the summary function:
<br>

```{r, echo = T, results = "markup"}
summary(acc_model_ehi)
```
<br>